---
title: "DV_RProject2"
author: "Probe, Yudkin, Honganen"
date: "Sunday, February 15, 2015"
output: html_document
---

##**Step 1:** Load the required packages and data

```{r}

source("../01 Data/Load_Packages.R", echo = TRUE)

source("../01 Data/Load_Data.R", echo = TRUE)


```

##**Step 2:** Display a subset of the dataframe

###Mortgage Backed Security Data
```{r}

tbl_df(df)

```

##**Step 3:** Display 3 Interesting Data Wrangling Sets / Visualizations

###Chart 1
This chart shows the amount of loans by type. Fix signifies a fixed rate loan and ARM signifies an adjustable rate mortgate.
```{r}
source("../02 Data Wrangling/DataWrangling1 - chart.R", echo = TRUE)
source("../03 Visualizations/DataWrangling1 - visualization.R", echo = TRUE)

```

###Chart 2
This chart filters the loans for Texas and California, provides a summary and then charts FICO vs. Orig_Rate
```{r}

source("../02 Data Wrangling/DataWrangling2 - chart.R", echo = TRUE)
source("../03 Visualizations/DataWrangling2 - visualization.R", echo = TRUE)

```

###Chart 3
This chart filters the loans for the top 50% according to the rate and then graphs CLTV vs. Interest Rate

```{r}

source("../02 Data Wrangling/DataWrangling3 - chart.R", echo = TRUE)
source("../03 Visualizations/DataWrangling3 - visualization.R", echo = TRUE)

```
